MinCall --- MinION basecaller pogonjen dubokim ucenjem

### 2017-05-05 paper/main.tex
Small changes...now it build the paper

\documentclass[times, utf8, seminar]{fer}
\usepackage{booktabs}

\usepackage{mathtools, amsmath,amsfonts,amssymb, amsthm}
\usepackage{acronym}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{float}
\usepackage{graphicx}
\graphicspath{ {Figures/} }

@@

\voditelj{Mile Sikić}
\title{CNNNano --- MinION  basecaller pogonjen dubokim ucenjem}
\engtitle{CNNNano --- MinION deep learning powered basecaller}
\author{Neven Miculinić}

@@

This model used advance state-of-the-art gated residual convolutional neural network, with top models having 270 layers and over 3M parameters, yet improvements over Metrichorn baseline are mariginal. As conclusion it might be that we've reached Bayesian error rate for R9 chemistry. Furthermore R9.5 and 1D^2 reads are under development which shall yield this paper's result obsolite quite soon, yet underlying code developed could easily be adjusted, and trained on new data.

@@

% \bibliographystyle{fer}
% \bibliographystyle{abbrv}
% \bibliography{refs}

>>>>

\documentclass[times, utf8, seminar, numeric]{fer}
\usepackage{booktabs}
\usepackage{mathtools, amsmath,amsfonts,amssymb, amsthm}
\usepackage{acronym}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{float}
\usepackage{graphicx}
\graphicspath{ {Figures/} }

@@

\voditelj{Mile Sikić}
\title{MinCall --- MinION  basecaller pogonjen dubokim ucenjem}
\engtitle{MinCall --- MinION deep learning powered basecaller}
\author{Neven Miculinić}

@@

This model used advance state-of-the-art gated residual convolutional neural network, with top models having 270 layers and over 3M parameters, yet improvements over Metrichorn baseline are mariginal. As conclusion it might be that we've reached Bayesian error rate for R9 chemistry. Furthermore R9.5 and 1D\^2 reads are under development which shall yield this paper's result obsolite quite soon, yet underlying code developed could easily be adjusted, and trained on new data.

@@

\bibliographystyle{fer}
\bibliography{refs}
% \bibliographystyle{abbrv}
